### 2024-01-09 paper/si_3_ml.tex
fix si section cross-ref

\subsection{d-band center and adsorption energy relations}

@@

\subsection{Feature correlation analysis}

@@

\subsection{Input pipeline construction}
The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
“numOrbitals” denotes the number of DOS orbitals,
and “numChannels” indicates the number of atomic channels.

@@

\subsection{Hyperparameter tuning for CNN}

@@

\subsection{Occlusion experiment}

@@

\subsection{Shifting experiment}

>>>>

\subsection{d-band center and adsorption energy relations}  \label{si_sec3.1_dband_eads}

@@

\subsection{Feature correlation analysis}  \label{si_sec3.2_feature_corr}

@@

\subsection{Input pipeline construction}  \label{si_sec3.3_input_pipeline}
The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
“numOrbitals” denotes the number of DOS orbitals,
and “numChannels” indicates the number of atomic channels.

@@

\subsection{Hyperparameter tuning for CNN}  \label{si_sec3.4_hyperparam}

@@

\subsection{Occlusion experiment}  \label{si_sec3.5_occlusion}

@@

\subsection{Shifting experiment}  \label{si_sec3.6_shifting}
